Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-03-05 paper_comparison/paper_comparison/paper_comparison.Rmd
hypotheses and p-value and power section modified

# Calculation of $p$-value and power

## Hypotheses

A paragraph on what hypothesis(es) are being tested.

Generally, by looking at the residuals we are concerned with

$H_o:$ The model specification is correct

against a broad alternative that something is missing:

$H_a:$ The model specification is not correct

The conventional tests are only equipped to measure specific departures, and thus have a more specific hypotheses being tested:

XXX

## $p$-value

@@

## Power

>>>>

# Calculation of statistical significance and test power

## What is being tested?

In diagnosing a model fit from residuals, we are generally interested in $H_0:$ *The regression model is correctly specified* against the broad alternative $H_a:$ *The regression model is misspecified*.

However, it is practically impossible to test this specific $H_0$ with conventional tests, which are constructed to measure specific departures. For example, the RESET test is formulated as $H_0:\gamma_1 = \gamma_2 = \gamma_3 = 0$ against $H_a: \gamma_1 \neq 0 \text{ or } \gamma_2 \neq 0 \text{ or } \gamma_3 \neq 0$, from $e = \gamma_1\hat{y}^2 + \gamma_2\hat{y}^3 + \gamma_3\hat{y}^4 + u, ~~u \sim N(0, \sigma_u^2)$. 
Similarly, the BP test is designed to specifically test $H_0:$ *error variances are all equal* ($\tau=0$) versus the alternative $H_a:$ *that the error variances are a multiplicative function of one or more variables* ($\tau\neq 0$) from $e^2 = \tau\hat{y} + u, ~ u\sim N(0,\sigma_u^2)$.

One of the potential benefits of the visual test, based on the lineup protocol, is that it should be able to detect a range of departures from good residuals.

## Statistical significance

@@

## Power of the tests

### 2023-03-05 paper_comparison/paper_comparison/paper_comparison.tex
hypotheses and p-value and power section modified

\hypertarget{calculation-of-p-value-and-power}{%
\section{\texorpdfstring{Calculation of \(p\)-value and
power}{Calculation of p-value and power}}\label{calculation-of-p-value-and-power}}

\hypertarget{hypotheses}{%
\subsection{Hypotheses}\label{hypotheses}}

A paragraph on what hypothesis(es) are being tested.

Generally, by looking at the residuals we are concerned with

\(H_o:\) The model specification is correct

against a broad alternative that something is missing:

\(H_a:\) The model specification is not correct

The conventional tests are only equipped to measure specific departures,
and thus have a more specific hypotheses being tested:

XXX

\hypertarget{p-value}{%
\subsection{\texorpdfstring{\(p\)-value}{p-value}}\label{p-value}}

@@

\hypertarget{power}{%
\subsection{Power}\label{power}}

>>>>

\hypertarget{calculation-of-statistical-significance-and-test-power}{%
\section{Calculation of statistical significance and test
power}\label{calculation-of-statistical-significance-and-test-power}}

\hypertarget{what-is-being-tested}{%
\subsection{What is being tested?}\label{what-is-being-tested}}

In diagnosing a model fit from residuals, we are generally interested in
\(H_0:\) \emph{The regression model is correctly specified} against the
broad alternative \(H_a:\) \emph{The regression model is misspecified}.

However, it is practically impossible to test this specific \(H_0\) with
conventional tests, which are constructed to measure specific
departures. For example, the RESET test is formulated as
\(H_0:\gamma_1 = \gamma_2 = \gamma_3 = 0\) against
\(H_a: \gamma_1 \neq 0 \text{ or } \gamma_2 \neq 0 \text{ or } \gamma_3 \neq 0\),
from
\(e = \gamma_1\hat{y}^2 + \gamma_2\hat{y}^3 + \gamma_3\hat{y}^4 + u, ~~u \sim N(0, \sigma_u^2)\).
Similarly, the BP test is designed to specifically test \(H_0:\)
\emph{error variances are all equal} (\(\tau=0\)) versus the alternative
\(H_a:\) \emph{that the error variances are a multiplicative function of
one or more variables} (\(\tau\neq 0\)) from
\(e^2 = \tau\hat{y} + u, ~ u\sim N(0,\sigma_u^2)\).

One of the potential benefits of the visual test, based on the lineup
protocol, is that it should be able to detect a range of departures from
good residuals.

\hypertarget{statistical-significance}{%
\subsection{Statistical significance}\label{statistical-significance}}

@@

\hypertarget{power-of-the-tests}{%
\subsection{Power of the tests}\label{power-of-the-tests}}
